---
title: "Build DiD Monthly Panel"
format: pdf
execute:
  echo: true
  warning: false
  message: false
---

## Construct DiD Panel

```{r}
library(dplyr)
library(stringr)
library(readr)
library(haven)
library(lubridate)

sum_or_na <- function(x) {
  if (all(is.na(x))) {
    NA_real_
  } else {
    sum(x, na.rm = TRUE)
  }
}

clean_digit_code <- function(x, width = NULL) {
  out <- str_replace_all(as.character(x), "[^0-9]", "")
  if (!is.null(width)) {
    out <- str_pad(out, width = width, side = "left", pad = "0")
  }
  out
}

pick_first_existing <- function(candidates, names_vec) {
  hit <- candidates[candidates %in% names_vec]
  if (length(hit) == 0) NA_character_ else hit[[1]]
}

panel_candidates <- c(
  "../../results/data/panel_hts10_monthly.csv",
  "panel_hts10_monthly.csv",
  "../../../panel_hts10_monthly.csv"
)
panel_path <- panel_candidates[file.exists(panel_candidates)][1]
if (is.na(panel_path)) {
  stop("Could not find panel_hts10_monthly.csv in expected paths.")
}

tar_candidates <- c(
  "../../../outside_data/data_files_aer_2013/tar_val.dta",
  "../../outside_data/data_files_aer_2013/tar_val.dta",
  "outside_data/data_files_aer_2013/tar_val.dta",
  "tar_val.dta",
  "../../../tar_val.dta"
)
tar_path <- tar_candidates[file.exists(tar_candidates)][1]
if (is.na(tar_path)) {
  stop("Could not find tar_val.dta in expected paths.")
}

cat("Using panel file:", panel_path, "\n")
cat("Using tariff file:", tar_path, "\n")

results_data_dir <- "../../results/data"
results_tables_did_dir <- "../../results/tables/did"
results_tables_event_study_dir <- "../../results/tables/event_study"
results_figures_event_study_dir <- "../../results/figures/event_study"
results_figures_seasonality_dir <- "../../results/figures/seasonality"

dir.create(results_data_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(results_tables_did_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(results_tables_event_study_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(results_figures_event_study_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(results_figures_seasonality_dir, recursive = TRUE, showWarnings = FALSE)

panel <- read_csv(panel_path, show_col_types = FALSE)
if (!"quantity_description" %in% names(panel)) {
  panel$quantity_description <- NA_character_
}

panel <- panel %>%
  mutate(
    Country = as.character(Country),
    hts10 = clean_digit_code(hts10, width = 10),
    date = as.Date(date),
    year = year(date),
    month_num = month(date),
    customs_value = suppressWarnings(as.numeric(customs_value)),
    first_unit_qty = suppressWarnings(as.numeric(first_unit_qty)),
    quantity_description = as.character(quantity_description)
  ) %>%
  filter(!is.na(date), !is.na(hts10), nchar(hts10) == 10)

# Restrict to China panel per design.
panel <- panel %>% filter(Country == "China")

# Drop known HTS10 codes with quantity-description switches.
problem_switch_hts10 <- c(
  "2607000020", "2711290060", "6111206050", "6111305050", "6111905050",
  "7115900530", "7115900590", "7115903000", "7115904000", "7115906000",
  "9001300000"
)

rows_before_drop <- nrow(panel)
panel <- panel %>% filter(!(hts10 %in% problem_switch_hts10))
rows_after_drop <- nrow(panel)

cat("Dropped rows from 11 problematic HTS10 codes:", rows_before_drop - rows_after_drop, "\n")

# Build HS8-month panel.
panel_hs8 <- panel %>%
  mutate(
    hs8 = str_sub(hts10, 1, 8),
    unit_label = if_else(is.na(quantity_description), "", str_trim(quantity_description))
  ) %>%
  group_by(hs8, date, year, month_num) %>%
  summarise(
    customs_value = sum_or_na(customs_value),
    unique_unit_count = n_distinct(unit_label[unit_label != ""]),
    unit_consistent = as.integer(unique_unit_count <= 1),
    quantity_description = case_when(
      unique_unit_count == 1 ~ first(unit_label[unit_label != ""]),
      TRUE ~ NA_character_
    ),
    first_unit_qty_hs8 = if_else(
      unique_unit_count <= 1,
      sum_or_na(first_unit_qty),
      NA_real_
    ),
    n_hts10_in_hs8 = n_distinct(hts10),
    .groups = "drop"
  ) %>%
  mutate(
    unit_value = if_else(
      !is.na(first_unit_qty_hs8) & first_unit_qty_hs8 > 0,
      customs_value / first_unit_qty_hs8,
      NA_real_
    )
  )

# Load tar_val and identify code + gap fields.
tar <- read_dta(tar_path) %>% as_tibble()
tar_names <- names(tar)

year_col <- pick_first_existing(c("year", "Year", "YEAR"), tar_names)
if (is.na(year_col)) stop("Could not identify year column in tar_val.dta.")

gap_col <- pick_first_existing(
  c("spread", "ntr_gap", "gap", "gap_pre", "NTR_gap"),
  tar_names
)
if (is.na(gap_col)) stop("Could not identify NTR-gap column in tar_val.dta.")

code_col <- pick_first_existing(
  c("hs10", "hts10", "hs8", "hts8", "hs"),
  tar_names
)
if (is.na(code_col)) {
  hs_like <- tar_names[str_detect(tolower(tar_names), "hs|hts|code")]
  if (length(hs_like) == 0) stop("Could not identify HS code column in tar_val.dta.")
  code_col <- hs_like[[1]]
}

value_col <- pick_first_existing(c("v", "value", "trade_value"), tar_names)

cat("tar_val fields selected -> code:", code_col, "| year:", year_col, "| gap:", gap_col, "\n")

tar_1999 <- tar %>%
  transmute(
    year = suppressWarnings(as.integer(.data[[year_col]])),
    code_raw = .data[[code_col]],
    gap = suppressWarnings(as.numeric(.data[[gap_col]])),
    weight_v = if (!is.na(value_col)) suppressWarnings(as.numeric(.data[[value_col]])) else NA_real_
  ) %>%
  filter(year == 1999) %>%
  mutate(
    code_digits = clean_digit_code(code_raw),
    hs8 = str_sub(str_pad(code_digits, width = 8, side = "left", pad = "0"), 1, 8)
  ) %>%
  filter(!is.na(gap), !is.na(hs8), nchar(hs8) == 8)

# Collapse to HS8 gap_pre (weighted by v when available, otherwise mean).
gap_pre_hs8 <- tar_1999 %>%
  group_by(hs8) %>%
  summarise(
    gap_pre = if (any(!is.na(weight_v) & weight_v > 0)) {
      sum(gap * if_else(is.na(weight_v), 0, weight_v), na.rm = TRUE) /
        sum(if_else(is.na(weight_v), 0, weight_v), na.rm = TRUE)
    } else {
      mean(gap, na.rm = TRUE)
    },
    .groups = "drop"
  )

# Merge gap_pre onto HS8-month trade panel.
did_panel <- panel_hs8 %>%
  left_join(gap_pre_hs8, by = "hs8")

# DiD indicators.
policy_date <- as.Date("2002-01-01")
median_gap <- median(did_panel$gap_pre, na.rm = TRUE)

did_panel <- did_panel %>%
  mutate(
    post = if_else(date >= policy_date, 1L, 0L),
    highgap = if_else(!is.na(gap_pre) & gap_pre >= median_gap, 1L, 0L, missing = NA_integer_),
    treated = if_else(!is.na(highgap), highgap * post, NA_integer_),
    event_time = (year(date) - year(policy_date)) * 12 + (month(date) - month(policy_date)),
    ln_customs_value = log1p(customs_value),
    ln_first_unit_qty = if_else(!is.na(first_unit_qty_hs8), log1p(first_unit_qty_hs8), NA_real_),
    ln_unit_value = if_else(!is.na(unit_value) & unit_value > 0, log(unit_value), NA_real_)
  ) %>%
  arrange(hs8, date)

# Duplicate-key check (hs8, date).
dup_count <- did_panel %>%
  count(hs8, date, name = "n") %>%
  filter(n > 1) %>%
  nrow()

# Save output.
did_panel_out <- file.path(results_data_dir, "did_panel_monthly.csv")
write_csv(did_panel, did_panel_out, na = "")
cat("\nSaved", did_panel_out, "\n")

# Diagnostics.
cat("\nDiagnostics\n")
cat("Rows:", nrow(did_panel), "\n")
cat("Unique hs8:", n_distinct(did_panel$hs8), "\n")
cat("Date range:", as.character(min(did_panel$date, na.rm = TRUE)), "to", as.character(max(did_panel$date, na.rm = TRUE)), "\n")
cat("Share unit_consistent==0:", mean(did_panel$unit_consistent == 0, na.rm = TRUE), "\n")
cat("Duplicate keys (hs8, date):", dup_count, "\n")

cat("\nSummary of gap_pre:\n")
print(summary(did_panel$gap_pre))

cat("\nHighgap counts:\n")
print(table(did_panel$highgap, useNA = "ifany"))

cat("\nSummary of customs_value (non-missing):\n")
print(summary(did_panel$customs_value[!is.na(did_panel$customs_value)]))

cat("\nSummary of unit_value (non-missing):\n")
print(summary(did_panel$unit_value[!is.na(did_panel$unit_value)]))
```

## Dropped Unit-Switch HTS10 Codes

Removed codes due to quantity-description switches (no conversion imposed):

- `2607000020`: kilograms (1996) -> component kilograms (2002)
- `2711290060`: no units collected (1996-2001) -> barrels (2002-2005)
- `6111206050`: dozens (2004) -> dozen pairs (2005)
- `6111305050`: dozens (2004) -> dozen pairs (2005)
- `6111905050`: dozens (2004) -> dozen pairs (2005)
- `7115900530`: no units collected (1999-2001) -> grams (2003, 2005 observed)
- `7115900590`: no units collected (2001) -> grams (2004-2005)
- `7115903000`: no units collected (1996-2001) -> grams (2002, 2004-2005 observed)
- `7115904000`: no units collected (1996-2001) -> grams (2002-2005)
- `7115906000`: no units collected (1997-2001) -> grams (2002-2005)
- `9001300000`: pairs (1999-2004 observed) -> number (2005)

## DiD Regression Ladder

```{r did-libs}
library(readr)
library(dplyr)
library(fixest)
```

```{r did-load-filter}
did_panel_candidates <- c(
  file.path(results_data_dir, "did_panel_monthly.csv"),
  "did_panel_monthly.csv"
)
did_panel_path <- did_panel_candidates[file.exists(did_panel_candidates)][1]
if (is.na(did_panel_path)) {
  stop("Could not find did_panel_monthly.csv in expected paths.")
}

df <- read_csv(did_panel_path, show_col_types = FALSE)

if (!"hs8" %in% names(df)) {
  stop("No hs8 column found.")
}

df <- df %>%
  mutate(
    product = as.character(hs8),
    date = as.Date(date)
  ) %>%
  filter(
    !is.na(product), !is.na(date),
    !is.na(post), !is.na(highgap)
  )

cat("Using panel file:", did_panel_path, "\n")
cat("Using product column: hs8\n")
cat("Rows in base sample:", nrow(df), "\n")
cat("Unique products in base sample:", n_distinct(df$product), "\n")

df_did_common <- df %>%
  filter(
    !is.na(ln_customs_value),
    !is.na(ln_first_unit_qty),
    !is.na(ln_unit_value),
    !is.na(month_num)
  )

cat("Rows in common DiD sample (all outcomes observed):", nrow(df_did_common), "\n")
cat("Unique products in common DiD sample:", n_distinct(df_did_common$product), "\n")
```

```{r did-ladder-customs}
cat("Rows in customs ladder sample (common sample):", nrow(df_did_common), "\n")

m1_customs <- feols(ln_customs_value ~ highgap * post, data = df_did_common, vcov = ~product)
m2_customs <- feols(ln_customs_value ~ highgap * post | product, data = df_did_common, vcov = ~product)
m3_customs <- feols(ln_customs_value ~ highgap * post | date, data = df_did_common, vcov = ~product)
m4_customs <- feols(ln_customs_value ~ highgap * post | product + date, data = df_did_common, vcov = ~product)
m5_customs <- feols(
  ln_customs_value ~ highgap * post + i(month_num, highgap, ref = 1) | product + date,
  data = df_did_common,
  vcov = ~product
)

etable(m1_customs, m2_customs, m3_customs, m4_customs, m5_customs)
out_customs <- file.path(results_tables_did_dir, "did_ladder_ln_customs_value.txt")
capture.output(
  etable(m1_customs, m2_customs, m3_customs, m4_customs, m5_customs),
  file = out_customs
)
cat("Saved", out_customs, "\n")
```

```{r did-ladder-quantity}
cat("Rows in quantity ladder sample (common sample):", nrow(df_did_common), "\n")

m1_qty <- feols(ln_first_unit_qty ~ highgap * post, data = df_did_common, vcov = ~product)
m2_qty <- feols(ln_first_unit_qty ~ highgap * post | product, data = df_did_common, vcov = ~product)
m3_qty <- feols(ln_first_unit_qty ~ highgap * post | date, data = df_did_common, vcov = ~product)
m4_qty <- feols(ln_first_unit_qty ~ highgap * post | product + date, data = df_did_common, vcov = ~product)
m5_qty <- feols(
  ln_first_unit_qty ~ highgap * post + i(month_num, highgap, ref = 1) | product + date,
  data = df_did_common,
  vcov = ~product
)

etable(m1_qty, m2_qty, m3_qty, m4_qty, m5_qty)
out_qty <- file.path(results_tables_did_dir, "did_ladder_ln_first_unit_qty.txt")
capture.output(
  etable(m1_qty, m2_qty, m3_qty, m4_qty, m5_qty),
  file = out_qty
)
cat("Saved", out_qty, "\n")
```

```{r did-ladder-unit-value}
cat("Rows in unit-value ladder sample (common sample):", nrow(df_did_common), "\n")

m1_uv <- feols(ln_unit_value ~ highgap * post, data = df_did_common, vcov = ~product)
m2_uv <- feols(ln_unit_value ~ highgap * post | product, data = df_did_common, vcov = ~product)
m3_uv <- feols(ln_unit_value ~ highgap * post | date, data = df_did_common, vcov = ~product)
m4_uv <- feols(ln_unit_value ~ highgap * post | product + date, data = df_did_common, vcov = ~product)
m5_uv <- feols(
  ln_unit_value ~ highgap * post + i(month_num, highgap, ref = 1) | product + date,
  data = df_did_common,
  vcov = ~product
)

etable(m1_uv, m2_uv, m3_uv, m4_uv, m5_uv)
out_uv <- file.path(results_tables_did_dir, "did_ladder_ln_unit_value.txt")
capture.output(
  etable(m1_uv, m2_uv, m3_uv, m4_uv, m5_uv),
  file = out_uv
)
cat("Saved", out_uv, "\n")
```

## Continuous-Treatment DiD (Gap Intensity)

```{r did-continuous-setup}
d_cont <- df %>%
  filter(!is.na(gap_pre))

d_unit_consistent <- d_cont %>%
  filter(unit_consistent == 1)

cat("Rows in continuous-treatment base sample:", nrow(d_cont), "\n")
cat("Unique products in continuous-treatment base sample:", n_distinct(d_cont$product), "\n")
cat("Rows in continuous-treatment unit-consistent sample:", nrow(d_unit_consistent), "\n")
cat("Unique products in continuous-treatment unit-consistent sample:", n_distinct(d_unit_consistent$product), "\n")
```

```{r did-continuous-run}
m_cv_cont <- feols(
  ln_customs_value ~ gap_pre * post | product + date,
  data = d_cont %>% filter(!is.na(ln_customs_value)),
  vcov = ~product
)

m_q_cont <- feols(
  ln_first_unit_qty ~ gap_pre * post | product + date,
  data = d_unit_consistent %>% filter(!is.na(ln_first_unit_qty)),
  vcov = ~product
)

m_uv_cont <- feols(
  ln_unit_value ~ gap_pre * post | product + date,
  data = d_unit_consistent %>% filter(!is.na(ln_unit_value)),
  vcov = ~product
)

etable(m_cv_cont, m_q_cont, m_uv_cont)
out_cont_models <- file.path(results_tables_did_dir, "did_continuous_gap_pre_models.txt")
capture.output(
  etable(m_cv_cont, m_q_cont, m_uv_cont),
  file = out_cont_models
)
cat("Saved", out_cont_models, "\n")

cont_effects <- tibble(
  outcome = c("ln_customs_value", "ln_first_unit_qty", "ln_unit_value"),
  coef_gap_pre_post = c(
    coef(m_cv_cont)[["gap_pre:post"]],
    coef(m_q_cont)[["gap_pre:post"]],
    coef(m_uv_cont)[["gap_pre:post"]]
  ),
  se_gap_pre_post = c(
    se(m_cv_cont)[["gap_pre:post"]],
    se(m_q_cont)[["gap_pre:post"]],
    se(m_uv_cont)[["gap_pre:post"]]
  ),
  n_obs = c(nobs(m_cv_cont), nobs(m_q_cont), nobs(m_uv_cont))
)
print(cont_effects)
out_cont_effects <- file.path(results_tables_did_dir, "did_continuous_gap_pre_post_effects.csv")
write_csv(cont_effects, out_cont_effects, na = "")
cat("Saved", out_cont_effects, "\n")
```

## Event Study

```{r event-study-settings}
df_customs <- df %>% filter(!is.na(ln_customs_value))
df_qty <- df %>% filter(!is.na(ln_first_unit_qty))
df_uv <- df %>% filter(!is.na(ln_unit_value))

WIN_PRE <- 60
WIN_POST <- 48

plot_event_study_year <- function(model_obj, output_png, y_label, win_pre, win_post, term_name = "highgap", base_year = 2002) {
  b <- coef(model_obj)
  s <- se(model_obj)

  coef_pattern <- paste0("^event_time::[-]?[0-9]+:", term_name, "$")
  parse_pattern <- paste0("^event_time::(-?[0-9]+):", term_name, "$")

  keep <- grepl(coef_pattern, names(b))
  if (!any(keep)) {
    stop("No event-study coefficients matched expected naming pattern.")
  }

  event_time <- as.integer(sub(parse_pattern, "\\1", names(b)[keep]))
  est <- as.numeric(b[keep])
  stderr <- as.numeric(s[keep])
  ci_low <- est - 1.96 * stderr
  ci_high <- est + 1.96 * stderr

  ord <- order(event_time)
  event_time <- event_time[ord]
  est <- est[ord]
  ci_low <- ci_low[ord]
  ci_high <- ci_high[ord]

  tick_min <- floor(min(event_time) / 12) * 12
  tick_max <- ceiling(max(event_time) / 12) * 12
  tick_at <- seq(tick_min, tick_max, by = 12)
  tick_labels <- base_year + tick_at / 12

  png(output_png, width = 1000, height = 700)
  plot(
    event_time, est,
    pch = 16,
    col = "black",
    xlab = "Year",
    ylab = y_label,
    xaxt = "n",
    ylim = range(c(ci_low, ci_high, 0), na.rm = TRUE)
  )
  segments(event_time, ci_low, event_time, ci_high, col = "gray40")
  lines(event_time, est, col = "black")
  axis(1, at = tick_at, labels = tick_labels)
  abline(h = 0, lty = 2, col = "red")
  dev.off()
}
```

```{r event-study-customs}
es_customs <- df_customs %>%
  filter(!is.na(event_time)) %>%
  filter(event_time >= -WIN_PRE, event_time <= WIN_POST)

cat("Rows in customs event-study sample:", nrow(es_customs), "\n")
cat("Customs event-time range:", min(es_customs$event_time), "to", max(es_customs$event_time), "\n")

m_es_customs_base <- feols(
  ln_customs_value ~ i(event_time, highgap, ref = -1) | product + date,
  data = es_customs,
  vcov = ~product
)

summary(m_es_customs_base)
out_es_customs <- file.path(results_figures_event_study_dir, "event_study_ln_customs_value.png")
plot_event_study_year(
  model_obj = m_es_customs_base,
  output_png = out_es_customs,
  y_label = "Effect on ln(1 + customs value)",
  win_pre = WIN_PRE,
  win_post = WIN_POST
)
cat("Saved", out_es_customs, "\n")
```

```{r event-study-quantity}
es_qty <- df_qty %>%
  filter(!is.na(event_time)) %>%
  filter(event_time >= -WIN_PRE, event_time <= WIN_POST)

cat("Rows in quantity event-study sample:", nrow(es_qty), "\n")
cat("Quantity event-time range:", min(es_qty$event_time), "to", max(es_qty$event_time), "\n")

m_es_qty_base <- feols(
  ln_first_unit_qty ~ i(event_time, highgap, ref = -1) | product + date,
  data = es_qty,
  vcov = ~product
)

summary(m_es_qty_base)
out_es_qty <- file.path(results_figures_event_study_dir, "event_study_ln_first_unit_qty.png")
plot_event_study_year(
  model_obj = m_es_qty_base,
  output_png = out_es_qty,
  y_label = "Effect on ln(1 + first unit quantity)",
  win_pre = WIN_PRE,
  win_post = WIN_POST
)
cat("Saved", out_es_qty, "\n")
```

```{r event-study-unit-value}
es_uv <- df_uv %>%
  filter(!is.na(event_time)) %>%
  filter(event_time >= -WIN_PRE, event_time <= WIN_POST)

cat("Rows in unit-value event-study sample:", nrow(es_uv), "\n")
cat("Unit-value event-time range:", min(es_uv$event_time), "to", max(es_uv$event_time), "\n")

m_es_uv_base <- feols(
  ln_unit_value ~ i(event_time, highgap, ref = -1) | product + date,
  data = es_uv,
  vcov = ~product
)

summary(m_es_uv_base)
out_es_uv <- file.path(results_figures_event_study_dir, "event_study_ln_unit_value.png")
plot_event_study_year(
  model_obj = m_es_uv_base,
  output_png = out_es_uv,
  y_label = "Effect on ln(unit value)",
  win_pre = WIN_PRE,
  win_post = WIN_POST
)
cat("Saved", out_es_uv, "\n")
```

## Continuous-Treatment Event Study (Gap Intensity)

```{r event-study-continuous-customs}
es_customs_cont <- d_cont %>%
  filter(!is.na(ln_customs_value), !is.na(event_time)) %>%
  filter(event_time >= -WIN_PRE, event_time <= WIN_POST)

cat("Rows in customs continuous event-study sample:", nrow(es_customs_cont), "\n")
cat("Customs continuous event-time range:", min(es_customs_cont$event_time), "to", max(es_customs_cont$event_time), "\n")

m_es_customs_cont <- feols(
  ln_customs_value ~ i(event_time, gap_pre, ref = -1) | product + date,
  data = es_customs_cont,
  vcov = ~product
)

pt_customs_cont <- wald(m_es_customs_cont, keep = "^event_time::-[0-9]+:gap_pre$")
cat("Customs pre-trend joint test (k < 0):\n")
print(pt_customs_cont)

out_es_cont_customs <- file.path(results_figures_event_study_dir, "event_study_continuous_ln_customs_value.png")
plot_event_study_year(
  model_obj = m_es_customs_cont,
  output_png = out_es_cont_customs,
  y_label = "Effect per +1 NTR gap on ln(1 + customs value)",
  win_pre = WIN_PRE,
  win_post = WIN_POST,
  term_name = "gap_pre"
)
cat("Saved", out_es_cont_customs, "\n")
```

```{r event-study-continuous-quantity}
es_qty_cont <- d_unit_consistent %>%
  filter(!is.na(ln_first_unit_qty), !is.na(event_time)) %>%
  filter(event_time >= -WIN_PRE, event_time <= WIN_POST)

cat("Rows in quantity continuous event-study sample:", nrow(es_qty_cont), "\n")
cat("Quantity continuous event-time range:", min(es_qty_cont$event_time), "to", max(es_qty_cont$event_time), "\n")

m_es_qty_cont <- feols(
  ln_first_unit_qty ~ i(event_time, gap_pre, ref = -1) | product + date,
  data = es_qty_cont,
  vcov = ~product
)

pt_qty_cont <- wald(m_es_qty_cont, keep = "^event_time::-[0-9]+:gap_pre$")
cat("Quantity pre-trend joint test (k < 0):\n")
print(pt_qty_cont)

out_es_cont_qty <- file.path(results_figures_event_study_dir, "event_study_continuous_ln_first_unit_qty.png")
plot_event_study_year(
  model_obj = m_es_qty_cont,
  output_png = out_es_cont_qty,
  y_label = "Effect per +1 NTR gap on ln(1 + first unit quantity)",
  win_pre = WIN_PRE,
  win_post = WIN_POST,
  term_name = "gap_pre"
)
cat("Saved", out_es_cont_qty, "\n")
```

```{r event-study-continuous-unit-value}
es_uv_cont <- d_unit_consistent %>%
  filter(!is.na(ln_unit_value), !is.na(event_time)) %>%
  filter(event_time >= -WIN_PRE, event_time <= WIN_POST)

cat("Rows in unit-value continuous event-study sample:", nrow(es_uv_cont), "\n")
cat("Unit-value continuous event-time range:", min(es_uv_cont$event_time), "to", max(es_uv_cont$event_time), "\n")

m_es_uv_cont <- feols(
  ln_unit_value ~ i(event_time, gap_pre, ref = -1) | product + date,
  data = es_uv_cont,
  vcov = ~product
)

pt_uv_cont <- wald(m_es_uv_cont, keep = "^event_time::-[0-9]+:gap_pre$")
cat("Unit-value pre-trend joint test (k < 0):\n")
print(pt_uv_cont)

out_es_cont_uv <- file.path(results_figures_event_study_dir, "event_study_continuous_ln_unit_value.png")
plot_event_study_year(
  model_obj = m_es_uv_cont,
  output_png = out_es_cont_uv,
  y_label = "Effect per +1 NTR gap on ln(unit value)",
  win_pre = WIN_PRE,
  win_post = WIN_POST,
  term_name = "gap_pre"
)
cat("Saved", out_es_cont_uv, "\n")
```

```{r event-study-continuous-save}
out_cont_es_models <- file.path(results_tables_event_study_dir, "event_study_continuous_gap_pre_models.txt")
capture.output(
  etable(m_es_customs_cont, m_es_qty_cont, m_es_uv_cont),
  file = out_cont_es_models
)
cat("Saved", out_cont_es_models, "\n")

cont_pretrend <- tibble(
  outcome = c("ln_customs_value", "ln_first_unit_qty", "ln_unit_value"),
  stat = c(pt_customs_cont$stat, pt_qty_cont$stat, pt_uv_cont$stat),
  p_value = c(pt_customs_cont$p, pt_qty_cont$p, pt_uv_cont$p),
  df1 = c(pt_customs_cont$df1, pt_qty_cont$df1, pt_uv_cont$df1),
  df2 = c(pt_customs_cont$df2, pt_qty_cont$df2, pt_uv_cont$df2),
  n_obs = c(nobs(m_es_customs_cont), nobs(m_es_qty_cont), nobs(m_es_uv_cont))
)
print(cont_pretrend)
out_cont_es_pretrend <- file.path(results_tables_event_study_dir, "event_study_continuous_gap_pre_pretrend_tests.csv")
write_csv(cont_pretrend, out_cont_es_pretrend, na = "")
cat("Saved", out_cont_es_pretrend, "\n")
```

## Seasonality Sanity Checks

```{r seasonality-sanity-helpers}
policy_date_sc <- as.Date("2002-01-01")

plot_pre_period_month_profile <- function(data, outcome_var, y_label, output_png) {
  pre_means <- data %>%
    filter(
      date < policy_date_sc,
      !is.na(highgap),
      !is.na(month_num),
      !is.na(.data[[outcome_var]])
    ) %>%
    group_by(highgap, month_num) %>%
    summarise(
      mean_outcome = mean(.data[[outcome_var]], na.rm = TRUE),
      n_obs = n(),
      .groups = "drop"
    )

  pre_means <- expand.grid(highgap = c(0L, 1L), month_num = 1:12) %>%
    left_join(pre_means, by = c("highgap", "month_num")) %>%
    arrange(highgap, month_num)

  low_gap <- pre_means %>% filter(highgap == 0L) %>% pull(mean_outcome)
  high_gap <- pre_means %>% filter(highgap == 1L) %>% pull(mean_outcome)

  png(output_png, width = 1000, height = 700)
  plot(
    1:12, low_gap,
    type = "o",
    pch = 16,
    col = "steelblue",
    xaxt = "n",
    xlab = "Month",
    ylab = y_label,
    ylim = range(c(low_gap, high_gap), na.rm = TRUE)
  )
  lines(1:12, high_gap, type = "o", pch = 17, col = "firebrick")
  axis(1, at = 1:12, labels = month.abb)
  abline(h = 0, lty = 2, col = "gray60")
  legend(
    "topright",
    legend = c("Low gap", "High gap"),
    col = c("steelblue", "firebrick"),
    pch = c(16, 17),
    lty = 1,
    bty = "n"
  )
  dev.off()

  cat("Saved", output_png, "\n")
  print(pre_means)
}

run_pre_period_month_interaction_test <- function(data, outcome_var, label) {
  pre_data <- data %>%
    filter(
      date < policy_date_sc,
      !is.na(highgap),
      !is.na(month_num),
      !is.na(.data[[outcome_var]])
    )

  model_formula <- as.formula(
    paste0(
      outcome_var,
      " ~ i(month_num, ref = 1) + i(month_num, highgap, ref = 1) | product + year"
    )
  )

  model <- feols(model_formula, data = pre_data, vcov = ~product)
  interaction_terms <- grep("^month_num::[0-9]+:highgap$", names(coef(model)), value = TRUE)

  if (length(interaction_terms) == 0) {
    stop("No highgap-by-month interaction terms found for ", label, ".")
  }

  cat("\nPre-period differential seasonality test for", label, "\n")
  print(wald(model, interaction_terms))
  invisible(model)
}
```

```{r seasonality-sanity-quantity}
out_seasonality_qty <- file.path(results_figures_seasonality_dir, "seasonality_preperiod_ln_first_unit_qty.png")
plot_pre_period_month_profile(
  data = df_qty,
  outcome_var = "ln_first_unit_qty",
  y_label = "Pre-2002 mean ln(1 + first unit quantity)",
  output_png = out_seasonality_qty
)

m_pre_month_qty <- run_pre_period_month_interaction_test(
  data = df_qty,
  outcome_var = "ln_first_unit_qty",
  label = "ln(1 + first unit quantity)"
)
```

```{r seasonality-sanity-unit-value}
out_seasonality_uv <- file.path(results_figures_seasonality_dir, "seasonality_preperiod_ln_unit_value.png")
plot_pre_period_month_profile(
  data = df_uv,
  outcome_var = "ln_unit_value",
  y_label = "Pre-2002 mean ln(unit value)",
  output_png = out_seasonality_uv
)

m_pre_month_uv <- run_pre_period_month_interaction_test(
  data = df_uv,
  outcome_var = "ln_unit_value",
  label = "ln(unit value)"
)
```
