---
title: "Rauch Homogeneous-Goods Robustness (HS8 Panel)"
format: pdf
execute:
  echo: true
  warning: false
  message: false
---

## Purpose

This notebook addresses heterogeneous-goods concerns by restricting to HS8 products whose HS6 parent maps to Rauch class `w` (organized exchange), and dropping products classified as `r` (reference priced) or `n` (differentiated).

Implementation follows the standard approach for HS8/HS10 panels:

1. Build `hs6_parent = substr(hs8, 1, 6)`.
2. Compute Rauch at HS6 using `concordance::get_proddiff`.
3. Merge HS6 Rauch labels back to HS8 and run:
   - Full-sample models.
   - `w`-only restricted models.

## Libraries and helpers

```{r setup}
library(readr)
library(dplyr)
library(tidyr)
library(stringr)
library(lubridate)
library(fixest)

if (!requireNamespace("concordance", quietly = TRUE)) {
  install.packages("concordance", repos = "https://cloud.r-project.org")
}
library(concordance)

clean_digit_code <- function(x, width = NULL) {
  out <- str_replace_all(as.character(x), "[^0-9]", "")
  if (!is.null(width)) {
    out <- str_pad(out, width = width, side = "left", pad = "0")
  }
  out
}

results_data_dir <- "../../results/data"
results_tables_dir <- "../../results/tables/rauch"
results_figures_dir <- "../../results/figures/rauch"

dir.create(results_data_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(results_tables_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(results_figures_dir, recursive = TRUE, showWarnings = FALSE)

did_panel_candidates <- c(
  file.path(results_data_dir, "did_panel_monthly.csv"),
  "../../../did_panel_monthly.csv"
)
did_panel_path <- did_panel_candidates[file.exists(did_panel_candidates)][1]
if (is.na(did_panel_path)) {
  stop("Could not find did_panel_monthly.csv in expected paths.")
}
```

## Load panel and build HS6 parents

```{r load-panel}
df <- read_csv(did_panel_path, show_col_types = FALSE) %>%
  mutate(
    hs8 = clean_digit_code(hs8, width = 8),
    hs6_parent = str_sub(hs8, 1, 6),
    product = as.character(hs8),
    date = as.Date(date),
    year = if_else(is.na(year), year(date), as.integer(year)),
    month_num = if_else(is.na(month_num), month(date), as.integer(month_num))
  ) %>%
  filter(
    !is.na(product), nchar(product) == 8,
    !is.na(hs6_parent), nchar(hs6_parent) == 6,
    !is.na(date), !is.na(post), !is.na(highgap)
  )

cat("Rows in base panel:", nrow(df), "\n")
cat("Unique HS8 products:", n_distinct(df$product), "\n")
cat("Unique HS6 parents:", n_distinct(df$hs6_parent), "\n")
cat("Using panel file:", did_panel_path, "\n")
```

## Compute Rauch at HS6 and merge back

```{r rauch-map}
hs6_unique <- sort(unique(df$hs6_parent))

w_share <- suppressWarnings(
  get_proddiff(sourcevar = hs6_unique, origin = "HS", setting = "CON", prop = "w")
)
r_share <- suppressWarnings(
  get_proddiff(sourcevar = hs6_unique, origin = "HS", setting = "CON", prop = "r")
)
n_share <- suppressWarnings(
  get_proddiff(sourcevar = hs6_unique, origin = "HS", setting = "CON", prop = "n")
)

rauch_hs6 <- tibble(
  hs6_parent = hs6_unique,
  w_share = as.numeric(w_share[hs6_unique]),
  r_share = as.numeric(r_share[hs6_unique]),
  n_share = as.numeric(n_share[hs6_unique])
  ) %>%
  mutate(
    rauch_class = case_when(
      is.na(w_share) | is.na(r_share) | is.na(n_share) ~ NA_character_,
      n_share >= w_share & n_share >= r_share ~ "n",
      w_share >= r_share & w_share >= n_share ~ "w",
      TRUE ~ "r"
    ),
    keep_wr = !is.na(rauch_class) & rauch_class %in% c("w", "r"),
    keep_w = !is.na(rauch_class) & rauch_class == "w"
  )

out_rauch_hs6 <- file.path(results_data_dir, "rauch_hs6_lookup.csv")
write_csv(rauch_hs6, out_rauch_hs6, na = "")
cat("Saved", out_rauch_hs6, "\n")

df_rauch <- df %>%
  left_join(rauch_hs6, by = "hs6_parent")

out_did_rauch <- file.path(results_data_dir, "did_panel_monthly_rauch.csv")
write_csv(df_rauch, out_did_rauch, na = "")
cat("Saved", out_did_rauch, "\n")

cat("\nRauch class counts (HS6 level):\n")
print(rauch_hs6 %>% count(rauch_class, keep_w, name = "n_hs6"))

cat("\nRauch class counts (observation level):\n")
print(df_rauch %>% count(rauch_class, keep_w, name = "n_obs"))

cat("\nShare of observations kept in w-only sample:\n")
print(mean(df_rauch$keep_w, na.rm = TRUE))
```

## DiD robustness: full sample vs Rauch w/r vs Rauch w-only

```{r did-robustness-functions}
run_did_compare <- function(data, outcome_var, output_txt_wr, output_txt_w, output_txt_compare, label) {
  data_full <- data %>% filter(!is.na(.data[[outcome_var]]))
  data_wr <- data_full %>% filter(keep_wr)
  data_w <- data_full %>% filter(keep_w)

  did_formula <- as.formula(
    paste0(
      outcome_var,
      " ~ highgap * post + i(month_num, highgap, ref = 1) | product + date"
    )
  )

  m_full <- feols(did_formula, data = data_full, vcov = ~product)
  m_wr <- feols(did_formula, data = data_wr, vcov = ~product)
  m_w <- feols(did_formula, data = data_w, vcov = ~product)

  cat("\n", label, "\n")
  cat("Rows full:", nrow(data_full), "| Rows w/r:", nrow(data_wr), "| Rows w-only:", nrow(data_w), "\n")
  comparison_table <- etable(m_full, m_wr, m_w)
  print(comparison_table)

  capture.output(
    comparison_table,
    file = output_txt_wr
  )
  capture.output(
    comparison_table,
    file = output_txt_w
  )
  capture.output(
    comparison_table,
    file = output_txt_compare
  )
  cat("Saved", output_txt_wr, "\n")
  cat("Saved", output_txt_w, "\n")
  cat("Saved", output_txt_compare, "\n")

  list(full = m_full, wr = m_wr, w = m_w)
}
```

```{r did-robustness-run}
did_customs <- run_did_compare(
  data = df_rauch,
  outcome_var = "ln_customs_value",
  output_txt_wr = file.path(results_tables_dir, "did_rauch_wr_ln_customs_value.txt"),
  output_txt_w = file.path(results_tables_dir, "did_rauch_w_ln_customs_value.txt"),
  output_txt_compare = file.path(results_tables_dir, "did_rauch_compare_ln_customs_value.txt"),
  label = "DiD: ln(1 + customs value)"
)

did_qty <- run_did_compare(
  data = df_rauch,
  outcome_var = "ln_first_unit_qty",
  output_txt_wr = file.path(results_tables_dir, "did_rauch_wr_ln_first_unit_qty.txt"),
  output_txt_w = file.path(results_tables_dir, "did_rauch_w_ln_first_unit_qty.txt"),
  output_txt_compare = file.path(results_tables_dir, "did_rauch_compare_ln_first_unit_qty.txt"),
  label = "DiD: ln(1 + first unit quantity)"
)

did_uv <- run_did_compare(
  data = df_rauch,
  outcome_var = "ln_unit_value",
  output_txt_wr = file.path(results_tables_dir, "did_rauch_wr_ln_unit_value.txt"),
  output_txt_w = file.path(results_tables_dir, "did_rauch_w_ln_unit_value.txt"),
  output_txt_compare = file.path(results_tables_dir, "did_rauch_compare_ln_unit_value.txt"),
  label = "DiD: ln(unit value)"
)
```

## Event-study robustness: full sample vs Rauch w-only sample

```{r event-study-helpers}
WIN_PRE <- 60
WIN_POST <- 48

plot_event_study_year <- function(model_obj, output_png, y_label, base_year = 2002) {
  b <- coef(model_obj)
  s <- se(model_obj)

  keep <- grepl("^event_time::[-]?[0-9]+:highgap$", names(b))
  if (!any(keep)) {
    stop("No event-study coefficients matched expected naming pattern.")
  }

  event_time <- as.integer(sub("^event_time::(-?[0-9]+):highgap$", "\\1", names(b)[keep]))
  est <- as.numeric(b[keep])
  stderr <- as.numeric(s[keep])
  ci_low <- est - 1.96 * stderr
  ci_high <- est + 1.96 * stderr

  ord <- order(event_time)
  event_time <- event_time[ord]
  est <- est[ord]
  ci_low <- ci_low[ord]
  ci_high <- ci_high[ord]

  tick_min <- floor(min(event_time) / 12) * 12
  tick_max <- ceiling(max(event_time) / 12) * 12
  tick_at <- seq(tick_min, tick_max, by = 12)
  tick_labels <- base_year + tick_at / 12

  png(output_png, width = 1000, height = 700)
  plot(
    event_time, est,
    pch = 16,
    col = "black",
    xlab = "Year",
    ylab = y_label,
    xaxt = "n",
    ylim = range(c(ci_low, ci_high, 0), na.rm = TRUE)
  )
  segments(event_time, ci_low, event_time, ci_high, col = "gray40")
  lines(event_time, est, col = "black")
  axis(1, at = tick_at, labels = tick_labels)
  abline(h = 0, lty = 2, col = "red")
  dev.off()
}

run_es_w <- function(data, outcome_var, y_label, output_stem) {
  es_full <- data %>%
    filter(
      !is.na(.data[[outcome_var]]),
      !is.na(event_time),
      event_time >= -WIN_PRE,
      event_time <= WIN_POST
    )

  es_wr <- es_full %>% filter(keep_wr)
  es_w <- es_full %>% filter(keep_w)

  es_formula <- as.formula(
    paste0(
      outcome_var,
      " ~ i(event_time, highgap, ref = -1) | product + date"
    )
  )

  m_full <- feols(es_formula, data = es_full, vcov = ~product)
  m_wr <- feols(es_formula, data = es_wr, vcov = ~product)
  m_w <- feols(es_formula, data = es_w, vcov = ~product)

  cat("\nEvent study:", y_label, "\n")
  cat("Rows full:", nrow(es_full), "| Rows w/r:", nrow(es_wr), "| Rows w-only:", nrow(es_w), "\n")
  print(etable(m_full, m_wr, m_w))

  out_txt <- file.path(results_tables_dir, paste0(output_stem, "_models.txt"))
  capture.output(etable(m_full, m_wr, m_w), file = out_txt)
  cat("Saved", out_txt, "\n")

  out_full_png <- file.path(results_figures_dir, paste0(output_stem, "_full.png"))
  out_wr_png <- file.path(results_figures_dir, paste0(output_stem, "_wr.png"))
  out_w_png <- file.path(results_figures_dir, paste0(output_stem, "_w.png"))

  plot_event_study_year(
    model_obj = m_full,
    output_png = out_full_png,
    y_label = paste0(y_label, " (full sample)")
  )
  plot_event_study_year(
    model_obj = m_wr,
    output_png = out_wr_png,
    y_label = paste0(y_label, " (Rauch w/r)")
  )
  plot_event_study_year(
    model_obj = m_w,
    output_png = out_w_png,
    y_label = paste0(y_label, " (Rauch w-only)")
  )
  cat("Saved", out_full_png, "\n")
  cat("Saved", out_wr_png, "\n")
  cat("Saved", out_w_png, "\n")

  list(full = m_full, wr = m_wr, w = m_w)
}
```

```{r event-study-run}
es_customs <- run_es_w(
  data = df_rauch,
  outcome_var = "ln_customs_value",
  y_label = "Effect on ln(1 + customs value)",
  output_stem = "event_study_rauch_ln_customs_value"
)

es_qty <- run_es_w(
  data = df_rauch,
  outcome_var = "ln_first_unit_qty",
  y_label = "Effect on ln(1 + first unit quantity)",
  output_stem = "event_study_rauch_ln_first_unit_qty"
)

es_uv <- run_es_w(
  data = df_rauch,
  outcome_var = "ln_unit_value",
  y_label = "Effect on ln(unit value)",
  output_stem = "event_study_rauch_ln_unit_value"
)
```

## Balance diagnostics (full vs w/r vs w)

```{r balance-settings}
EVENT_MIN <- -60
EVENT_MAX <- 48
PRE_POLICY_DATE <- as.Date("2002-01-01")

samples <- list(
  full = df_rauch,
  wr = df_rauch %>% filter(keep_wr),
  w = df_rauch %>% filter(keep_w)
)
```

```{r cluster-balance-overall}
overall_balance <- bind_rows(lapply(names(samples), function(sample_name) {
  d <- samples[[sample_name]]
  product_balance <- d %>% distinct(product, highgap)

  n_obs <- nrow(d)
  n_products <- nrow(product_balance)
  n_treated_products <- sum(product_balance$highgap == 1, na.rm = TRUE)
  n_control_products <- sum(product_balance$highgap == 0, na.rm = TRUE)

  tibble(
    sample = sample_name,
    n_obs = n_obs,
    n_products = n_products,
    n_treated_products = n_treated_products,
    n_control_products = n_control_products,
    treated_share_product = if_else(n_products > 0, n_treated_products / n_products, NA_real_),
    treated_share_obs = mean(d$highgap == 1, na.rm = TRUE)
  )
}))

cat("Overall treated/control balance by cluster:\n")
print(overall_balance)
out_balance_overall <- file.path(results_data_dir, "rauch_balance_overall.csv")
write_csv(overall_balance, out_balance_overall, na = "")
cat("Saved", out_balance_overall, "\n")
```

```{r cluster-balance-event-time}
event_balance <- bind_rows(lapply(names(samples), function(sample_name) {
  d <- samples[[sample_name]] %>%
    filter(
      !is.na(event_time),
      event_time >= EVENT_MIN,
      event_time <= EVENT_MAX
    )

  d %>%
    group_by(event_time) %>%
    summarise(
      n_obs = n(),
      treated_rows = sum(highgap == 1, na.rm = TRUE),
      control_rows = sum(highgap == 0, na.rm = TRUE),
      treated_products = n_distinct(product[highgap == 1]),
      control_products = n_distinct(product[highgap == 0]),
      .groups = "drop"
    ) %>%
    mutate(sample = sample_name, .before = 1)
})) %>%
  arrange(sample, event_time)

event_balance_flags <- event_balance %>%
  group_by(sample) %>%
  summarise(
    n_bins = n(),
    bins_treated_products_lt10 = sum(treated_products < 10, na.rm = TRUE),
    bins_treated_products_lt5 = sum(treated_products < 5, na.rm = TRUE),
    min_treated_products = min(treated_products, na.rm = TRUE),
    median_treated_products = median(treated_products, na.rm = TRUE),
    max_treated_products = max(treated_products, na.rm = TRUE),
    .groups = "drop"
  )

cat("Event-time treated/control product balance summary:\n")
print(event_balance_flags)
out_event_bins <- file.path(results_data_dir, "rauch_balance_event_time_bins.csv")
out_event_flags <- file.path(results_data_dir, "rauch_balance_event_time_flags.csv")
write_csv(event_balance, out_event_bins, na = "")
write_csv(event_balance_flags, out_event_flags, na = "")
cat("Saved", out_event_bins, "\n")
cat("Saved", out_event_flags, "\n")
```

## Exposure balance diagnostics (`gap_pre` and `highgap`)

```{r exposure-balance}
highgap_balance <- bind_rows(lapply(names(samples), function(sample_name) {
  d <- samples[[sample_name]]
  product_balance <- d %>% distinct(product, highgap)

  tibble(
    sample = sample_name,
    n_obs = nrow(d),
    n_products = nrow(product_balance),
    highgap_share_obs = mean(d$highgap == 1, na.rm = TRUE),
    highgap_share_product = mean(product_balance$highgap == 1, na.rm = TRUE)
  )
}))

gap_quantiles <- bind_rows(lapply(names(samples), function(sample_name) {
  d <- samples[[sample_name]] %>%
    distinct(product, gap_pre, highgap) %>%
    filter(!is.na(gap_pre), !is.na(highgap))

  d %>%
    group_by(highgap) %>%
    summarise(
      sample = sample_name,
      n_products = n(),
      q00 = quantile(gap_pre, 0.00, na.rm = TRUE),
      q10 = quantile(gap_pre, 0.10, na.rm = TRUE),
      q25 = quantile(gap_pre, 0.25, na.rm = TRUE),
      q50 = quantile(gap_pre, 0.50, na.rm = TRUE),
      q75 = quantile(gap_pre, 0.75, na.rm = TRUE),
      q90 = quantile(gap_pre, 0.90, na.rm = TRUE),
      q100 = quantile(gap_pre, 1.00, na.rm = TRUE),
      .groups = "drop"
    ) %>%
    mutate(group = if_else(highgap == 1, "highgap", "lowgap"), .before = highgap)
})) %>%
  arrange(sample, highgap)

full_median_gap_pre <- median(df_rauch$gap_pre, na.rm = TRUE)

highgap_definition_check <- bind_rows(lapply(names(samples), function(sample_name) {
  d <- samples[[sample_name]] %>%
    filter(!is.na(gap_pre), !is.na(highgap))

  sample_median_gap_pre <- median(d$gap_pre, na.rm = TRUE)
  implied_highgap_full_median <- as.integer(d$gap_pre >= full_median_gap_pre)
  implied_highgap_sample_median <- as.integer(d$gap_pre >= sample_median_gap_pre)

  tibble(
    sample = sample_name,
    full_median_gap_pre = full_median_gap_pre,
    sample_median_gap_pre = sample_median_gap_pre,
    mismatch_vs_full_median = sum(d$highgap != implied_highgap_full_median, na.rm = TRUE),
    mismatch_if_recomputed_in_sample = sum(d$highgap != implied_highgap_sample_median, na.rm = TRUE),
    n_checked = nrow(d)
  )
}))

cat("Highgap balance summary:\n")
print(highgap_balance)

cat("\nGap_pre quantiles by highgap group:\n")
print(gap_quantiles)

cat("\nHighgap-definition check (full-median indicator should match observed highgap):\n")
print(highgap_definition_check)

out_highgap_balance <- file.path(results_data_dir, "rauch_highgap_balance.csv")
out_gap_quantiles <- file.path(results_data_dir, "rauch_gap_pre_quantiles_by_group.csv")
out_highgap_def <- file.path(results_data_dir, "rauch_highgap_definition_check.csv")
write_csv(highgap_balance, out_highgap_balance, na = "")
write_csv(gap_quantiles, out_gap_quantiles, na = "")
write_csv(highgap_definition_check, out_highgap_def, na = "")
cat("Saved", out_highgap_balance, "\n")
cat("Saved", out_gap_quantiles, "\n")
cat("Saved", out_highgap_def, "\n")
```

## Pre-2002 outcome balance diagnostics

```{r preperiod-balance}
outcome_specs <- tibble(
  outcome_var = c("ln_customs_value", "ln_first_unit_qty", "ln_unit_value"),
  outcome_label = c("ln(1 + customs value)", "ln(1 + first unit quantity)", "ln(unit value)")
)

preperiod_means <- bind_rows(lapply(names(samples), function(sample_name) {
  d <- samples[[sample_name]] %>% filter(date < PRE_POLICY_DATE)

  bind_rows(lapply(seq_len(nrow(outcome_specs)), function(i) {
    outcome_var <- outcome_specs$outcome_var[[i]]

    stats_by_group <- d %>%
      filter(!is.na(.data[[outcome_var]]), !is.na(highgap)) %>%
      group_by(highgap) %>%
      summarise(
        mean_outcome = mean(.data[[outcome_var]], na.rm = TRUE),
        n_obs = n(),
        n_products = n_distinct(product),
        .groups = "drop"
      ) %>%
      mutate(group = if_else(highgap == 1, "highgap", "lowgap"))

    stats_wide <- stats_by_group %>%
      select(group, mean_outcome, n_obs, n_products) %>%
      pivot_wider(
        names_from = group,
        values_from = c(mean_outcome, n_obs, n_products),
        names_sep = "_"
      )

    mean_low <- if ("mean_outcome_lowgap" %in% names(stats_wide)) stats_wide$mean_outcome_lowgap[[1]] else NA_real_
    mean_high <- if ("mean_outcome_highgap" %in% names(stats_wide)) stats_wide$mean_outcome_highgap[[1]] else NA_real_

    tibble(
      sample = sample_name,
      outcome = outcome_var,
      mean_lowgap = mean_low,
      mean_highgap = mean_high,
      diff_high_minus_low = mean_high - mean_low,
      n_obs_lowgap = if ("n_obs_lowgap" %in% names(stats_wide)) stats_wide$n_obs_lowgap[[1]] else NA_real_,
      n_obs_highgap = if ("n_obs_highgap" %in% names(stats_wide)) stats_wide$n_obs_highgap[[1]] else NA_real_,
      n_products_lowgap = if ("n_products_lowgap" %in% names(stats_wide)) stats_wide$n_products_lowgap[[1]] else NA_real_,
      n_products_highgap = if ("n_products_highgap" %in% names(stats_wide)) stats_wide$n_products_highgap[[1]] else NA_real_
    )
  }))
}))

cat("Pre-2002 means by highgap:\n")
print(preperiod_means)
out_preperiod_means <- file.path(results_data_dir, "rauch_pre2002_means_by_highgap.csv")
write_csv(preperiod_means, out_preperiod_means, na = "")
cat("Saved", out_preperiod_means, "\n")
```

```{r preperiod-month-profiles}
plot_preperiod_month_profile <- function(outcome_var, outcome_label, output_png) {
  profile_data <- bind_rows(lapply(names(samples), function(sample_name) {
    d <- samples[[sample_name]] %>%
      filter(
        date < PRE_POLICY_DATE,
        !is.na(.data[[outcome_var]]),
        !is.na(highgap),
        !is.na(month_num)
      ) %>%
      group_by(highgap, month_num) %>%
      summarise(
        mean_outcome = mean(.data[[outcome_var]], na.rm = TRUE),
        .groups = "drop"
      ) %>%
      mutate(sample = sample_name, .before = 1)

    d
  }))

  month_diff <- profile_data %>%
    select(sample, month_num, highgap, mean_outcome) %>%
    mutate(group = if_else(highgap == 1, "highgap", "lowgap")) %>%
    select(-highgap) %>%
    pivot_wider(names_from = group, values_from = mean_outcome) %>%
    mutate(diff_high_minus_low = highgap - lowgap, outcome = outcome_var, .before = 1)

  out_month_diff <- file.path(results_data_dir, paste0("rauch_pre2002_month_diff_", outcome_var, ".csv"))
  write_csv(month_diff, out_month_diff, na = "")
  cat("Saved", out_month_diff, "\n")

  png(output_png, width = 1400, height = 450)
  par(mfrow = c(1, 3), mar = c(4, 4, 3, 1))
  for (sample_name in names(samples)) {
    plot_df <- profile_data %>% filter(sample == sample_name)

    grid_df <- expand.grid(highgap = c(0L, 1L), month_num = 1:12) %>%
      left_join(plot_df, by = c("highgap", "month_num")) %>%
      arrange(highgap, month_num)

    low_vals <- grid_df %>% filter(highgap == 0L) %>% pull(mean_outcome)
    high_vals <- grid_df %>% filter(highgap == 1L) %>% pull(mean_outcome)

    plot(
      1:12, low_vals,
      type = "o",
      pch = 16,
      col = "steelblue",
      xaxt = "n",
      xlab = "Month",
      ylab = outcome_label,
      ylim = range(c(low_vals, high_vals), na.rm = TRUE),
      main = paste("Sample:", sample_name)
    )
    lines(1:12, high_vals, type = "o", pch = 17, col = "firebrick")
    axis(1, at = 1:12, labels = month.abb)
    legend(
      "topright",
      legend = c("lowgap", "highgap"),
      col = c("steelblue", "firebrick"),
      pch = c(16, 17),
      lty = 1,
      bty = "n",
      cex = 0.85
    )
  }
  dev.off()

  diff_summary <- month_diff %>%
    group_by(sample, outcome) %>%
    summarise(
      diff_min = min(diff_high_minus_low, na.rm = TRUE),
      diff_max = max(diff_high_minus_low, na.rm = TRUE),
      diff_sd = sd(diff_high_minus_low, na.rm = TRUE),
      .groups = "drop"
    )

  list(diff_summary = diff_summary)
}

month_diff_summaries <- bind_rows(lapply(seq_len(nrow(outcome_specs)), function(i) {
  outcome_var <- outcome_specs$outcome_var[[i]]
  outcome_label <- outcome_specs$outcome_label[[i]]
  output_png <- file.path(results_figures_dir, paste0("rauch_pre2002_month_profile_", outcome_var, ".png"))

  out <- plot_preperiod_month_profile(
    outcome_var = outcome_var,
    outcome_label = outcome_label,
    output_png = output_png
  )
  cat("Saved", output_png, "\n")

  out$diff_summary
}))

cat("Month-profile high-low difference summary:\n")
print(month_diff_summaries)
out_month_diff_summary <- file.path(results_data_dir, "rauch_pre2002_month_diff_summary.csv")
write_csv(month_diff_summaries, out_month_diff_summary, na = "")
cat("Saved", out_month_diff_summary, "\n")
```

## Event-study precision sensitivity: drop `i(month_num, highgap)`

```{r es-precision-sensitivity}
run_es_precision_diagnostics <- function(data, sample_name, outcome_var) {
  d <- data %>%
    filter(
      !is.na(.data[[outcome_var]]),
      !is.na(event_time),
      event_time >= EVENT_MIN,
      event_time <= EVENT_MAX
    )

  spec_formulas <- list(
    with_month_interactions = as.formula(
      paste0(
        outcome_var,
        " ~ i(event_time, highgap, ref = -1) + i(month_num, highgap, ref = 1) | product + date"
      )
    ),
    event_time_only = as.formula(
      paste0(
        outcome_var,
        " ~ i(event_time, highgap, ref = -1) | product + date"
      )
    )
  )

  bind_rows(lapply(names(spec_formulas), function(spec_name) {
    model <- suppressWarnings(feols(spec_formulas[[spec_name]], data = d, vcov = ~product))

    coef_names <- names(coef(model))
    keep_event <- grepl("^event_time::[-]?[0-9]+:highgap$", coef_names)
    event_se <- se(model)[keep_event]

    tibble(
      sample = sample_name,
      outcome = outcome_var,
      spec = spec_name,
      n_obs = nrow(d),
      n_products = n_distinct(d$product),
      n_treated_products = n_distinct(d$product[d$highgap == 1]),
      n_event_coeff = sum(keep_event),
      n_collinear_dropped = length(model$collin.var),
      event_se_min = min(event_se, na.rm = TRUE),
      event_se_p10 = as.numeric(quantile(event_se, 0.10, na.rm = TRUE)),
      event_se_median = median(event_se, na.rm = TRUE),
      event_se_p90 = as.numeric(quantile(event_se, 0.90, na.rm = TRUE)),
      event_se_max = max(event_se, na.rm = TRUE),
      n_event_se_gt_100 = sum(event_se > 100, na.rm = TRUE)
    )
  }))
}

es_precision_diag <- bind_rows(lapply(names(samples), function(sample_name) {
  bind_rows(lapply(outcome_specs$outcome_var, function(outcome_var) {
    run_es_precision_diagnostics(
      data = samples[[sample_name]],
      sample_name = sample_name,
      outcome_var = outcome_var
    )
  }))
}))

es_precision_compare <- es_precision_diag %>%
  select(sample, outcome, spec, event_se_median, event_se_p90, n_event_se_gt_100, n_collinear_dropped) %>%
  pivot_wider(
    names_from = spec,
    values_from = c(event_se_median, event_se_p90, n_event_se_gt_100, n_collinear_dropped)
  ) %>%
  mutate(
    median_se_ratio_with_vs_without_month = event_se_median_with_month_interactions / event_se_median_event_time_only,
    p90_se_ratio_with_vs_without_month = event_se_p90_with_month_interactions / event_se_p90_event_time_only
  ) %>%
  arrange(sample, outcome)

cat("Event-study precision diagnostics by sample/spec:\n")
print(es_precision_diag)

cat("\nSE-collapse comparison (with month interactions vs event-time only):\n")
print(es_precision_compare)

out_es_precision_diag <- file.path(results_data_dir, "rauch_event_study_precision_diagnostics.csv")
out_es_precision_compare <- file.path(results_data_dir, "rauch_event_study_precision_compare.csv")
write_csv(es_precision_diag, out_es_precision_diag, na = "")
write_csv(es_precision_compare, out_es_precision_compare, na = "")
cat("Saved", out_es_precision_diag, "\n")
cat("Saved", out_es_precision_compare, "\n")
```
